---
title: "Assignment B1"
author: "Xin Wang"
date: "2023-10-21"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Section for Libraries

```{r}
library(dplyr)
library(testthat)
```


## Exercise 1: Make a Function (25 points)
In this exercise, you’ll be making a function and fortifying it. The function need not be complicated. The function need not be “serious”, but shouldn’t be nonsense.

_This function accepts arguments for grouping variables and summary statistics, handle NA values, and utilize the ellipsis (...) to allow for various summary functions._


## Exercise 2: Document your Function (20 points)
In the same code chunk where you made your function, document the function using roxygen2 tags.

```{r}
#' Summarize Data by Group
#'
#' This function performs group-wise summarization of a data frame based on
#' specified grouping variables and summary statistics.
#'
#' @param data A data frame that contains the data to be summarized.
#' @param group_vars A character vector of grouping variables. These variables
#'        will be used to group the data.
#' @param ... A set of summary expressions using the "name = expression" format.
#'        These expressions will be applied to the columns in the data frame.
#'
#' @return A data frame with grouped summaries, where each group is defined by
#'         the specified grouping variables. The summary statistics for each
#'         column are calculated based on the expressions provided.

summarize_data <- function(data, group_vars, ...) {
  summary_exprs <- rlang::enquos(...)
  
  result <- dplyr::group_by(data, dplyr::across(dplyr::all_of(group_vars), .names = "group"))
  result <- dplyr::summarise(result, !!!summary_exprs, .groups = "drop")
  
  return(result)
}

```


## Exercise 3: Include examples (15 points)
Demonstrate the usage of your function with a few examples. Use one or more new code chunks, describing what you’re doing.

1. I create a data frame called `STAT_545_grades` with columns for course parts, work numbers, worksheet grades, and assignment grades.

2. I use function, `summarize_data`, to group and summarize this data. Specifically, I group the data by `course_part` and calculate the mean of `worksheet_grade` and the sum of `assignment_grade` for each group, while ignoring missing values.

3. The result is stored in the `result` variable and displayed in the console. It provides summaries of grades by course part.

```{r}
STAT_545_grades <- data.frame(
  course_part = c("A", "A", "B", "B"),
  work_number = c("1", "3", "1", "3"),
  worksheet_grade = c(10, 9, 8, NA),
  assignment_grade = c(36, 78, 25, 27)
)

# Usage of the summarize_data function
result <- summarize_data(STAT_545_grades, group_vars = c("course_part"), 
                        mean_worksheet_grade = mean(worksheet_grade, na.rm = TRUE),
                        sum_assignment_grade = sum(assignment_grade, na.rm = TRUE))

result
```


## Exercise 4: Test the Function (25 points)
Write formal tests for your function. You should use at least three non-redundant uses of an expect_() function from the testthat package, and they should be contained in a test_that() function (or more than one). They should all pass.

```{r}
# Test case 1: Vector with no NAs
test_that("Test Case 1: Vector with No NAs", {
  data <- data.frame(
    Group = c("A", "A", "B", "B"),
    Value = c(10, 15, 20, 25)
  )
  result <- summarize_data(data, group_vars = "Group", Mean_Value = mean(Value))
  expected_result <- data.frame(Group = c("A", "B"), Mean_Value = c(12.5, 22.5))
  expect_true(all.equal(result, expected_result, check.attributes = FALSE))
})

# Test case 2: Vector with NAs
test_that("Test Case 2: Vector with NAs", {
  data <- data.frame(
    Group = c("A", "A", "B", "B"),
    Value = c(10, 15, NA, 25)
  )
  result <- summarize_data(data, group_vars = "Group", Mean_Value = mean(Value, na.rm = TRUE))
  expected_result <- data.frame(Group = c("A", "B"), Mean_Value = c(12.5, 25))
  expect_equal(result$Mean_Value, expected_result$Mean_Value)
})

# Test Case 3: Vector of length 0
test_that("Test Case 3: Vector of Length 0", {
  data <- data.frame(
    Group = character(0),
    Value = numeric(0)
  )
  result <- summarize_data(data, group_vars = "Group", Mean_Value = mean(Value, na.rm = TRUE))
  expect_length(result$Mean_Value, 0)
})
```

